---
title: "About me"
output:
    distill::distill_article:
      toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(distilltools)
```

Welcome to my personal website! I am a +6 months of experience as a data analyst in a social-tech company. Practiced experience in data cleaning, visualization, and analysis with R, SQL, Tableau, and communication. He working on personal projects over different cases in data analysis. Attending online courses and reading books to leverage my knowledge.

<center>
```{r, echo=FALSE}
icon_link(
    text = "Resume",
    url  = "https://docs.google.com/document/d/1ySz7KR_ZjWB4NO6u24l9M9BfP6VDiU8m/edit?usp=sharing&ouid=104673057248975950615&rtpof=true&sd=true"
)
```
</center>

### Short Bio
Welcome to my personal website! I am a +6 months of experience as a data analyst in a social-tech company. Practiced experience in data cleaning, visualization, and analysis with R, SQL, Tableau, and communication. He working on personal projects over different cases in data analysis. Attending online courses and reading books to leverage my knowledge.

### `r make_icon("fab fa-r-project")` Programming
Welcome to my personal website! I am a +6 months of experience as a data analyst in a social-tech company. Practiced experience in data cleaning, visualization, and analysis with R, SQL, Tableau, and communication. He working on personal projects over different cases in data analysis. Attending online courses and reading books to leverage my knowledge.

### Mountaineering
Welcome to my personal website! I am a +6 months of experience as a data analyst in a social-tech company. Practiced experience in data cleaning, visualization, and analysis with R, SQL, Tableau, and communication. He working on personal projects over different cases in data analysis. Attending online courses and reading books to leverage my knowledge.

### Football
Welcome to my personal website! I am a +6 months of experience as a data analyst in a social-tech company. Practiced experience in data cleaning, visualization, and analysis with R, SQL, Tableau, and communication. He working on personal projects over different cases in data analysis. Attending online courses and reading books to leverage my knowledge.

### Music
Welcome to my personal website! I am a +6 months of experience as a data analyst in a social-tech company. Practiced experience in data cleaning, visualization, and analysis with R, SQL, Tableau, and communication. He working on personal projects over different cases in data analysis. Attending online courses and reading books to leverage my knowledge.
